The Inner Mass-Ratio Distribution of Intermediate-Mass Stars

### 2016-01-26 paper/ms.tex
Added a few columns to the companion table
Added component and Nobs columns to companions table

@@

TODO: Describe imaging observations (band, observation time, etc). Add a table for this!

@@

  HIP 118243 &            B1V &     23:59:0.54 &   +55:45:17.74 &  6583.74 &       TS23 &      351 &    1760 \\

@@

\begin{longtable*}{|l|lrrll|}
\hline
       star &      $T_\mathrm{eff}$ &   $v\sin{i}$ &  [Fe/H] &   Isochrone Mass &   Spectral Type Mass \\
\hline
\endhead
\hline
\multicolumn{3}{r}{{Continued on next page}} \\
\endfoot
   HIP 2548 &  $5732 \pm 112$ &      30 &    -0.5 &  $1.0^{+0.06}_{-0.04}$ &  $1.0^{+0.04}_{-0.03}$ \\
   HIP 3478 &  $5524 \pm 150$ &       5 &    -0.5 &  $1.1^{+0.28}_{-0.13}$ &  $1.0^{+0.03}_{-0.04}$ \\
   HIP 5310 &  $3343 \pm 154$ &      30 &     0.0 &  $0.3^{+0.13}_{-0.08}$ &  $0.4^{+0.12}_{-0.12}$ \\
     HR 545 &   $4312 \pm 87$ &       5 &    -0.5 &  $0.8^{+0.11}_{-0.10}$ &  $0.7^{+0.01}_{-0.02}$ \\
     HR 604 &  $4736 \pm 150$ &       5 &     0.5 &    $nan^{+nan}_{-nan}$ &  $0.8^{+0.02}_{-0.02}$ \\
  HIP 10732 &  $5578 \pm 109$ &       5 &     0.0 &  $1.0^{+0.29}_{-0.04}$ &  $1.0^{+0.02}_{-0.04}$ \\
  HIP 12332 &  $5551 \pm 107$ &      10 &     0.0 &    $nan^{+nan}_{-nan}$ &  $1.0^{+0.01}_{-0.04}$ \\
  HIP 12706 &  $6051 \pm 107$ &      10 &     0.0 &  $1.1^{+0.03}_{-0.03}$ &  $1.1^{+0.04}_{-0.05}$ \\
  HIP 13165 &  $5773 \pm 163$ &       5 &    -0.5 &  $1.1^{+0.31}_{-0.08}$ &  $1.0^{+0.10}_{-0.03}$ \\
  HIP 13327 &  $5524 \pm 150$ &       5 &    -0.5 &  $1.2^{+0.20}_{-0.21}$ &  $1.0^{+0.03}_{-0.04}$ \\
  HIP 14576 &  $6980 \pm 103$ &      10 &     0.0 &  $1.4^{+0.03}_{-0.03}$ &  $1.5^{+0.05}_{-0.03}$ \\
  HIP 14764 &  $5601 \pm 108$ &      30 &     0.5 &    $nan^{+nan}_{-nan}$ &  $1.0^{+0.03}_{-0.03}$ \\
  HIP 16244 &  $5592 \pm 107$ &       5 &    -0.5 &  $1.2^{+0.20}_{-0.22}$ &  $1.0^{+0.03}_{-0.03}$ \\
  HIP 16340 &  $6214 \pm 150$ &       5 &    -0.5 &  $1.2^{+0.29}_{-0.07}$ &  $1.2^{+0.06}_{-0.05}$ \\
  HIP 16611 &  $5476 \pm 154$ &       1 &     0.5 &  $0.9^{+0.04}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
  HIP 17563 &  $8574 \pm 147$ &       5 &     0.5 &  $1.9^{+0.25}_{-0.11}$ &  $2.0^{+0.05}_{-0.06}$ \\
  HIP 18396 &  $4492 \pm 162$ &      30 &    -0.5 &  $0.9^{+0.10}_{-0.12}$ &  $0.8^{+0.03}_{-0.02}$ \\
  HIP 18724 &  $6831 \pm 154$ &      20 &     0.0 &  $1.7^{+0.13}_{-0.23}$ &  $1.4^{+0.04}_{-0.04}$ \\
  HIP 19949 &  $6492 \pm 155$ &      20 &    -0.5 &  $1.3^{+0.06}_{-0.05}$ &  $1.3^{+0.06}_{-0.06}$ \\
  HIP 20380 &  $6492 \pm 109$ &      20 &    -0.5 &  $1.3^{+0.04}_{-0.04}$ &  $1.3^{+0.03}_{-0.05}$ \\
  HIP 21589 &  $4562 \pm 154$ &       5 &     0.0 &  $0.7^{+0.04}_{-0.03}$ &  $0.8^{+0.02}_{-0.03}$ \\
  HIP 22833 &  $4745 \pm 107$ &      10 &     0.0 &  $0.8^{+0.02}_{-0.02}$ &  $0.8^{+0.02}_{-0.01}$ \\
  HIP 22958 &  $6126 \pm 112$ &      30 &    -0.5 &  $1.4^{+0.22}_{-0.21}$ &  $1.2^{+0.04}_{-0.04}$ \\
  HIP 23362 &  $6283 \pm 158$ &       5 &    -0.5 &  $1.2^{+0.06}_{-0.05}$ &  $1.2^{+0.07}_{-0.05}$ \\
  HIP 23916 &  $5450 \pm 158$ &       5 &    -0.5 &  $1.1^{+0.20}_{-0.20}$ &  $0.9^{+0.04}_{-0.03}$ \\
  HIP 24244 &  $4929 \pm 158$ &       5 &    -0.5 &  $0.8^{+0.04}_{-0.04}$ &  $0.8^{+0.02}_{-0.03}$ \\
  HIP 24902 &  $5679 \pm 154$ &      30 &     0.0 &  $1.0^{+0.05}_{-0.04}$ &  $1.0^{+0.04}_{-0.03}$ \\
  HIP 25143 &  $5883 \pm 109$ &      30 &     0.0 &  $1.1^{+0.04}_{-0.03}$ &  $1.1^{+0.05}_{-0.07}$ \\
  HIP 26126 &   $5841 \pm 91$ &       5 &    -0.5 &  $1.0^{+0.03}_{-0.03}$ &  $1.0^{+0.05}_{-0.04}$ \\
  HIP 32607 &   $5068 \pm 91$ &       5 &    -0.5 &  $0.8^{+0.02}_{-0.02}$ &  $0.9^{+0.01}_{-0.01}$ \\
  HIP 37450 &   $nan \pm nan$ & \nodata & \nodata &    $nan^{+nan}_{-nan}$ &    $nan^{+nan}_{-nan}$ \\
  HIP 38538 &  $6576 \pm 150$ &      30 &    -0.5 &  $1.3^{+0.05}_{-0.05}$ &  $1.3^{+0.10}_{-0.05}$ \\
  HIP 38593 &  $5398 \pm 112$ &       5 &    -0.5 &  $1.3^{+0.08}_{-0.13}$ &  $0.9^{+0.03}_{-0.03}$ \\
  HIP 38846 &  $6595 \pm 158$ &      10 &     0.0 &  $1.7^{+0.12}_{-0.21}$ &  $1.3^{+0.09}_{-0.05}$ \\
  HIP 39847 &  $5750 \pm 107$ &      10 &    -0.5 &  $1.0^{+0.04}_{-0.03}$ &  $1.0^{+0.05}_{-0.03}$ \\
  HIP 40881 &  $4562 \pm 154$ &      10 &    -0.5 &  $0.8^{+0.18}_{-0.05}$ &  $0.8^{+0.02}_{-0.03}$ \\
  HIP 42129 &  $5241 \pm 158$ &      10 &    -0.5 &  $1.2^{+0.12}_{-0.18}$ &  $0.9^{+0.04}_{-0.02}$ \\
  HIP 46283 &   $9268 \pm 85$ &      10 &     0.5 &    $nan^{+nan}_{-nan}$ &  $2.2^{+0.02}_{-0.02}$ \\
  HIP 51362 &  $5033 \pm 158$ &       5 &    -0.5 &  $0.8^{+0.04}_{-0.04}$ &  $0.8^{+0.02}_{-0.03}$ \\
  HIP 52678 &  $5033 \pm 112$ &      10 &    -0.5 &  $1.0^{+0.16}_{-0.19}$ &  $0.8^{+0.01}_{-0.02}$ \\
  HIP 55266 &  $8483 \pm 139$ &      30 &    -0.5 &  $1.8^{+0.06}_{-0.04}$ &  $2.0^{+0.06}_{-0.05}$ \\
  HIP 63945 &  $7038 \pm 162$ &      10 &    -0.5 &  $1.6^{+0.26}_{-0.16}$ &  $1.5^{+0.08}_{-0.06}$ \\
  HIP 72154 &  $4918 \pm 162$ &      30 &    -0.5 &  $0.9^{+0.22}_{-0.09}$ &  $0.8^{+0.03}_{-0.03}$ \\
  HIP 76267 &  $5449 \pm 158$ &       5 &    -0.5 &  $0.9^{+0.04}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
  HIP 77336 &  $6407 \pm 112$ &      20 &     0.0 &  $1.2^{+0.04}_{-0.04}$ &  $1.3^{+0.04}_{-0.05}$ \\
  HIP 77516 &  $6825 \pm 141$ &       5 &     0.5 &  $1.4^{+0.21}_{-0.06}$ &  $1.4^{+0.03}_{-0.04}$ \\
  HIP 78820 &  $5658 \pm 158$ &       5 &    -0.5 &  $1.3^{+0.11}_{-0.13}$ &  $1.0^{+0.04}_{-0.04}$ \\
  HIP 78821 &  $4968 \pm 154$ &      10 &    -0.5 &  $1.1^{+0.09}_{-0.10}$ &  $0.8^{+0.02}_{-0.03}$ \\
  HIP 79199 &  $4616 \pm 158$ &       5 &    -0.5 &  $0.9^{+0.14}_{-0.14}$ &  $0.8^{+0.02}_{-0.03}$ \\
  HIP 79404 &  $4773 \pm 112$ &      10 &    -0.5 &  $1.1^{+0.07}_{-0.08}$ &  $0.8^{+0.02}_{-0.01}$ \\
  HIP 80460 &  $6391 \pm 155$ &      10 &     0.0 &  $1.2^{+0.06}_{-0.05}$ &  $1.3^{+0.06}_{-0.06}$ \\
  HIP 82673 &  $4668 \pm 112$ &       5 &     0.5 &  $0.8^{+0.03}_{-0.03}$ &  $0.8^{+0.01}_{-0.02}$ \\
  HIP 84606 &  $5476 \pm 154$ &      10 &    -0.5 &  $0.9^{+0.05}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
  HIP 85379 &  $7590 \pm 151$ &      20 &     0.0 &    $nan^{+nan}_{-nan}$ &  $1.7^{+0.05}_{-0.03}$ \\
  HIP 85998 &   $5460 \pm 91$ &       1 &    -0.5 &  $1.0^{+0.28}_{-0.03}$ &  $0.9^{+0.04}_{-0.01}$ \\
  HIP 88116 &  $5293 \pm 112$ &       5 &     0.0 &  $0.9^{+0.03}_{-0.03}$ &  $0.9^{+0.02}_{-0.03}$ \\
  HIP 88818 &   $5296 \pm 91$ &      20 &    -0.5 &  $0.9^{+0.02}_{-0.02}$ &  $0.9^{+0.02}_{-0.03}$ \\
  HIP 88817 &  $3647 \pm 154$ &      20 &     0.0 &  $0.5^{+0.07}_{-0.10}$ &  $0.5^{+0.03}_{-0.05}$ \\
  HIP 91118 &  $6492 \pm 155$ &      10 &    -0.5 &  $1.3^{+0.26}_{-0.07}$ &  $1.3^{+0.06}_{-0.06}$ \\
  HIP 93805 &  $4054 \pm 109$ &       5 &    -0.5 &  $0.6^{+0.03}_{-0.03}$ &  $0.6^{+0.04}_{-0.02}$ \\
  HIP 96840 &  $9942 \pm 152$ &      10 &     0.0 &    $nan^{+nan}_{-nan}$ &  $2.3^{+0.03}_{-0.01}$ \\
 HIP 100221 &  $5273 \pm 154$ &      20 &    -0.5 &  $0.9^{+0.29}_{-0.07}$ &  $0.9^{+0.04}_{-0.03}$ \\
 HIP 100907 &  $5222 \pm 109$ &      10 &     0.0 &  $0.9^{+0.03}_{-0.03}$ &  $0.9^{+0.04}_{-0.02}$ \\
 HIP 103298 &   $4615 \pm 90$ &       5 &    -0.5 &  $0.7^{+0.02}_{-0.02}$ &  $0.8^{+0.01}_{-0.02}$ \\
 HIP 109139 &  $5710 \pm 112$ &      20 &    -0.5 &  $1.0^{+0.04}_{-0.03}$ &  $1.0^{+0.03}_{-0.03}$ \\
 HIP 109521 &   $4412 \pm 87$ &      10 &     0.0 &  $0.7^{+0.02}_{-0.02}$ &  $0.7^{+0.01}_{-0.01}$ \\
 HIP 115115 &   $4943 \pm 91$ &       5 &    -0.5 &  $0.8^{+0.02}_{-0.02}$ &  $0.8^{+0.02}_{-0.02}$ \\
 \label{tab:companions}

>>>>

As part of the follow-up effort, we used the NIRI instrument behind the Altair adaptive optics system at the Gemini North Telescope. We obtained 25 images in 5 dithering positions in the K-continuum band centered on $2.2718\ \mu m$, with a variety of exposure times and dates listed in Table \ref{tab:imaging_obs}. Because the targets are all extremely bright, we used the high read noise and high flux detector settings to allow for very short co-add exposure times. We reduced the data using the Gemini set of IRAF[TODO: Add iraf footnote] tasks, which include steps for nonlinearity correction, flat-fielding, sky subtraction, and co-addition of the dither frames.

@@

@@

  HIP 118243 &            B1V &     23:59:0.54 &   +55:45:17.74 &  6583.74 &       TS23 &      351 &    1760

@@

\begin{deluxetable}{|l|lll|}
\tabletypesize{\small}
\tablewidth{0pt}
\tablecaption{NIRI Observation log}
\tablehead{
       \colhead{star} &  \colhead{Kmag} &        \colhead{date} & \colhead{Exposure}
       }

\startdata
  HIP 22833 &  4.83 &  2015-03-29 &   50x0.3 \\
  HIP 22958 &  5.79 &  2015-10-19 &   52x0.4 \\
  HIP 23916 &  5.98 &  2015-04-05 &   18x1.1 \\
  HIP 26093 &  5.96 &  2015-03-23 &   33x0.6 \\
  HIP 26126 &  5.07 &  2015-03-29 &   40x0.4 \\
  HIP 29735 &  5.10 &  2015-03-22 &   83x0.2 \\
  HIP 31278 &  5.46 &  2015-03-28 &   29x0.6 \\
  HIP 38538 &  4.66 &  2015-10-19 &   75x0.2 \\
  HIP 39847 &  4.66 &  2015-03-27 &   50x0.3 \\
  HIP 75178 &  5.49 &  2015-03-24 &   29x0.6 \\
  HIP 88116 &  4.47 &  2015-03-22 &   50x0.3 \\
  HIP 91118 &  5.67 &  2015-10-16 &   43x0.4 \\
 HIP 100221 &  5.70 &  2015-10-18 &   26x0.7 \\
 HIP 100907 &  5.41 &  2015-10-16 &   43x0.4 \\
 HIP 101909 &  $6.47^{\dagger}$ &  2015-10-16 &   39x0.5 \\
 HIP 109139 &  4.40 &  2015-04-26 &   50x0.3 \\
 HIP 109521 &  4.96 &  2015-04-25 &   40x0.4 \\
 HIP 115115 &  4.96 &  2015-10-18 &   40x0.4 \\
 HIP 118243 &  $5.87^{\dagger}$ &  2015-07-23 &   58x0.3 \\
\enddata
\tablecomments{$\dagger$: There is no K-magnitude tabulated in the Simbad Database. The value quoted here is estimated from the spectral type of the star and its V-band magnitude.}
\label{tab:imaging_obs}
\end{deluxetable}

\clearpage
\newpage

\LongTables
\begin{deluxetable*}{|l|rrlrrrll|}
\tabletypesize{\small}
\tablewidth{0pt}
\tablecaption{Companion Detections}
\tablehead{
       \colhead{star} & \colhead{component} & \colhead{$N_\mathrm{obs}$}   &   \colhead{$T_\mathrm{eff}$} &   \colhead{$v\sin{i}$} &  \colhead{[Fe/H]} & \colhead{$\Delta K$} &   \colhead{Isochrone Mass} &   \colhead{Spectral Type Mass}
       }

\startdata
   HIP 2548 & Aa,Ab &     2 &  $5732 \pm 112$ &      30 &    -0.5 &          0 &  $1.0^{+0.06}_{-0.04}$ &  $1.0^{+0.04}_{-0.03}$ \\
   HIP 5310 & AB &     1 &  $3343 \pm 154$ &      30 &     0.0 &          0 &  $0.3^{+0.13}_{-0.08}$ &  $0.4^{+0.12}_{-0.12}$ \\
     HR 545 & Aa,Ab$^{\dagger}$ &     3 &   $4312 \pm 87$ &       5 &    -0.5 &          0 &  $0.8^{+0.11}_{-0.10}$ &  $0.7^{+0.01}_{-0.02}$ \\
     HR 604 & AB &     1 &  $4736 \pm 150$ &       5 &     0.5 &          0 &    $nan^{+nan}_{-nan}$ &  $0.8^{+0.02}_{-0.02}$ \\
  HIP 10732 & AB$^{\dagger}$ &     2 &  $5578 \pm 109$ &       5 &     0.0 &          0 &  $1.0^{+0.29}_{-0.04}$ &  $1.0^{+0.02}_{-0.04}$ \\
  HIP 12332 & AB$^{\dagger}$ &     2 &  $5551 \pm 107$ &      10 &     0.0 &          0 &    $nan^{+nan}_{-nan}$ &  $1.0^{+0.01}_{-0.04}$ \\
  HIP 12706 & AB &     2 &  $6051 \pm 107$ &      10 &     0.0 &          0 &  $1.1^{+0.03}_{-0.03}$ &  $1.1^{+0.04}_{-0.05}$ \\
  HIP 13165 & AB? &     1 &  $5773 \pm 163$ &       5 &    -0.5 &          0 &  $1.1^{+0.31}_{-0.08}$ &  $1.0^{+0.10}_{-0.03}$ \\
  HIP 13327 & AB$^{\dagger}$ &     1 &  $5524 \pm 150$ &       5 &    -0.5 &          0 &  $1.2^{+0.20}_{-0.21}$ &  $1.0^{+0.03}_{-0.04}$ \\
  HIP 14576 & Aa,Ab &     2 &  $6980 \pm 103$ &      10 &     0.0 &          0 &  $1.4^{+0.03}_{-0.03}$ &  $1.5^{+0.05}_{-0.03}$ \\
  HIP 14764 & AB$^{\dagger}$ &     2 &  $5601 \pm 108$ &      30 &     0.5 &          0 &    $nan^{+nan}_{-nan}$ &  $1.0^{+0.03}_{-0.03}$ \\
  HIP 16244 & AB &     2 &  $5592 \pm 107$ &       5 &    -0.5 &          0 &  $1.2^{+0.20}_{-0.22}$ &  $1.0^{+0.03}_{-0.03}$ \\
  HIP 16340 & AB$^{\dagger}$ &     1 &  $6214 \pm 150$ &       5 &    -0.5 &          0 &  $1.2^{+0.29}_{-0.07}$ &  $1.2^{+0.06}_{-0.05}$ \\
  HIP 16611 & AB &     1 &  $5476 \pm 154$ &       1 &     0.5 &          0 &  $0.9^{+0.04}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
  HIP 17563 & AB &     1 &  $8574 \pm 147$ &       5 &     0.5 &          0 &  $1.9^{+0.25}_{-0.11}$ &  $2.0^{+0.05}_{-0.06}$ \\
  HIP 18724 & AB &     1 &  $6831 \pm 154$ &      20 &     0.0 &          0 &  $1.7^{+0.13}_{-0.23}$ &  $1.4^{+0.04}_{-0.04}$ \\
  HIP 19949 & AB$^{\dagger}$ &     1 &  $6492 \pm 155$ &      20 &    -0.5 &          0 &  $1.3^{+0.06}_{-0.05}$ &  $1.3^{+0.06}_{-0.06}$ \\
  HIP 20380 & AB$^{\dagger}$ &     2 &  $6492 \pm 109$ &      20 &    -0.5 &          0 &  $1.3^{+0.04}_{-0.04}$ &  $1.3^{+0.03}_{-0.05}$ \\
  HIP 21589 & Aa,Ab? &     1? &  $4562 \pm 154$ &       5 &     0.0 &          0 &  $0.7^{+0.04}_{-0.03}$ &  $0.8^{+0.02}_{-0.03}$ \\
  HIP 22833 & AB &     2 &  $4745 \pm 107$ &      10 &     0.0 &          0 &  $0.8^{+0.02}_{-0.02}$ &  $0.8^{+0.02}_{-0.01}$ \\
  HIP 22958 & Aa,Ab &     2 &  $6126 \pm 112$ &      30 &    -0.5 &          0 &  $1.4^{+0.22}_{-0.21}$ &  $1.2^{+0.04}_{-0.04}$ \\
  HIP 23362 & AB$^{\dagger}$ &     1 &  $6283 \pm 158$ &       5 &    -0.5 &          0 &  $1.2^{+0.06}_{-0.05}$ &  $1.2^{+0.07}_{-0.05}$ \\
  HIP 23916 & Aa,Ab$^{\dagger}$ &     1 &  $5450 \pm 158$ &       5 &    -0.5 &          0 &  $1.1^{+0.20}_{-0.20}$ &  $0.9^{+0.04}_{-0.03}$ \\
  HIP 24902 & AB &     1 &  $5679 \pm 154$ &      30 &     0.0 &          0 &  $1.0^{+0.05}_{-0.04}$ &  $1.0^{+0.04}_{-0.03}$ \\
  HIP 25143 & AB$^{\dagger}$ &     2 &  $5883 \pm 109$ &      30 &     0.0 &          0 &  $1.1^{+0.04}_{-0.03}$ &  $1.1^{+0.05}_{-0.07}$ \\
  HIP 26126 & AB? &     3 &   $5841 \pm 91$ &       5 &    -0.5 &          0 &  $1.0^{+0.03}_{-0.03}$ &  $1.0^{+0.05}_{-0.04}$ \\
  HIP 32607 & AB$^{\dagger}$ &     3 &   $5068 \pm 91$ &       5 &    -0.5 &          0 &  $0.8^{+0.02}_{-0.02}$ &  $0.9^{+0.01}_{-0.01}$ \\
  HIP 37450 & AB$^{\dagger}$ &     1 &   $nan \pm nan$ & \nodata & \nodata &          0 &    $nan^{+nan}_{-nan}$ &    $nan^{+nan}_{-nan}$ \\
  HIP 38593 & AB$^{\dagger}$ &     2 &  $5398 \pm 112$ &       5 &    -0.5 &          0 &  $1.3^{+0.08}_{-0.13}$ &  $0.9^{+0.03}_{-0.03}$ \\
  HIP 38846 & AB$^{\dagger}$ &     1 &  $6595 \pm 158$ &      10 &     0.0 &          0 &  $1.7^{+0.12}_{-0.21}$ &  $1.3^{+0.09}_{-0.05}$ \\
  HIP 39847 & Aa,Ab$^{\dagger}$ &     2 &  $5750 \pm 107$ &      10 &    -0.5 &          0 &  $1.0^{+0.04}_{-0.03}$ &  $1.0^{+0.05}_{-0.03}$ \\
  HIP 40881 & AB$^{\dagger}$ &     1 &  $4562 \pm 154$ &      10 &    -0.5 &          0 &  $0.8^{+0.18}_{-0.05}$ &  $0.8^{+0.02}_{-0.03}$ \\
  HIP 42129 & AB &     1 &  $5241 \pm 158$ &      10 &    -0.5 &          0 &  $1.2^{+0.12}_{-0.18}$ &  $0.9^{+0.04}_{-0.02}$ \\
  HIP 46283 & AB? &     3 &   $9268 \pm 85$ &      10 &     0.5 &          0 &    $nan^{+nan}_{-nan}$ &  $2.2^{+0.02}_{-0.02}$ \\
  HIP 55266 & AB &     1 &  $8483 \pm 139$ &      30 &    -0.5 &          0 &  $1.8^{+0.06}_{-0.04}$ &  $2.0^{+0.06}_{-0.05}$ \\
  HIP 63945 & Aa,Ab or AC? &     1 &  $7038 \pm 162$ &      10 &    -0.5 &          0 &  $1.6^{+0.26}_{-0.16}$ &  $1.5^{+0.08}_{-0.06}$ \\
  HIP 72154 & AB$^{\dagger}$ &     1 &  $4918 \pm 162$ &      30 &    -0.5 &          0 &  $0.9^{+0.22}_{-0.09}$ &  $0.8^{+0.03}_{-0.03}$ \\
  HIP 76267 & AB &     1 &  $5449 \pm 158$ &       5 &    -0.5 &          0 &  $0.9^{+0.04}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
  HIP 77336 & AB$^{\dagger}$ &     2 &  $6407 \pm 112$ &      20 &     0.0 &          0 &  $1.2^{+0.04}_{-0.04}$ &  $1.3^{+0.04}_{-0.05}$ \\
  HIP 77516 & AB &     1 &  $6825 \pm 141$ &       5 &     0.5 &          0 &  $1.4^{+0.21}_{-0.06}$ &  $1.4^{+0.03}_{-0.04}$ \\
  HIP 78820 & AB &     1 &  $5658 \pm 158$ &       5 &    -0.5 &          0 &  $1.3^{+0.11}_{-0.13}$ &  $1.0^{+0.04}_{-0.04}$ \\
  HIP 79199 & AB &     1 &  $4616 \pm 158$ &       5 &    -0.5 &          0 &  $0.9^{+0.14}_{-0.14}$ &  $0.8^{+0.02}_{-0.03}$ \\
  HIP 79404 & AB$^{\dagger}$ &     2 &  $4773 \pm 112$ &      10 &    -0.5 &          0 &  $1.1^{+0.07}_{-0.08}$ &  $0.8^{+0.02}_{-0.01}$ \\
  HIP 80460 & AB &     1 &  $6391 \pm 155$ &      10 &     0.0 &          0 &  $1.2^{+0.06}_{-0.05}$ &  $1.3^{+0.06}_{-0.06}$ \\
  HIP 82673 & AB$^{\dagger}$ &     2 &  $4668 \pm 112$ &       5 &     0.5 &          0 &  $0.8^{+0.03}_{-0.03}$ &  $0.8^{+0.01}_{-0.02}$ \\
  HIP 84606 & AB &     1 &  $5476 \pm 154$ &      10 &    -0.5 &          0 &  $0.9^{+0.05}_{-0.04}$ &  $0.9^{+0.04}_{-0.03}$ \\
  HIP 88116 & AB$^{\dagger}$ &     2 &  $5293 \pm 112$ &       5 &     0.0 &          0 &  $0.9^{+0.03}_{-0.03}$ &  $0.9^{+0.02}_{-0.03}$ \\
  HIP 88818 & Aa,Ab &     3 &   $5296 \pm 91$ &      20 &    -0.5 &          0 &  $0.9^{+0.02}_{-0.02}$ &  $0.9^{+0.02}_{-0.03}$ \\
  HIP 88817 & Aa,Ab &     1 &  $3647 \pm 154$ &      20 &     0.0 &          0 &  $0.5^{+0.07}_{-0.10}$ &  $0.5^{+0.03}_{-0.05}$ \\
  HIP 91118 & AB &     1 &  $6492 \pm 155$ &      10 &    -0.5 &          0 &  $1.3^{+0.26}_{-0.07}$ &  $1.3^{+0.06}_{-0.06}$ \\
  HIP 93805 & Aa,Ab$^{\dagger}$ &     2 &  $4054 \pm 109$ &       5 &    -0.5 &          0 &  $0.6^{+0.03}_{-0.03}$ &  $0.6^{+0.04}_{-0.02}$ \\
  HIP 96840 & AB &     1 &  $9942 \pm 152$ &      10 &     0.0 &          0 &    $nan^{+nan}_{-nan}$ &  $2.3^{+0.03}_{-0.01}$ \\
 HIP 100221 & AB &     1 &  $5273 \pm 154$ &      20 &    -0.5 &          0 &  $0.9^{+0.29}_{-0.07}$ &  $0.9^{+0.04}_{-0.03}$ \\
 HIP 100907 & AB$^{\dagger}$ &     2 &  $5222 \pm 109$ &      10 &     0.0 &          0 &  $0.9^{+0.03}_{-0.03}$ &  $0.9^{+0.04}_{-0.02}$ \\
 HIP 103298 & Aa,Ab &     3 &   $4615 \pm 90$ &       5 &    -0.5 &          0 &  $0.7^{+0.02}_{-0.02}$ &  $0.8^{+0.01}_{-0.02}$ \\
 HIP 109139 & AB &     2 &  $5710 \pm 112$ &      20 &    -0.5 &          0 &  $1.0^{+0.04}_{-0.03}$ &  $1.0^{+0.03}_{-0.03}$ \\
 HIP 109521 & Aa,Ab$^{\dagger}$ &     3 &   $4412 \pm 87$ &      10 &     0.0 &          0 &  $0.7^{+0.02}_{-0.02}$ &  $0.7^{+0.01}_{-0.01}$ \\
 HIP 115115 & AB &     3 &   $4943 \pm 91$ &       5 &    -0.5 &          0 &  $0.8^{+0.02}_{-0.02}$ &  $0.8^{+0.02}_{-0.02}$

 \enddata

 \tablecomments{$\dagger$: Newly discovered companions.}
 \label{tab:companions}
\end{deluxetable*}

\clearpage
\newpage
